---
title: "Fantasy Football Data Exploration"
output: 
  html_notebook:
    code_folding: hide
    toc: true
    toc_float: true
---

# Introduction

The following is an analysis of the "Will Carter Bowl" fantasy football league. The data was scraped from FleaFlicker.com using an  a python script written with BS4.

The goal is to "tackle" the following questions:

  * Team/Manager Performance and Style Metrics
    * Power Rankings (smoothed mean variation of points)
    * Efficiency
    * Variation
    * Lineup Errors
        * Starting players on BYE
        * Starting no one in a position slot
        * Starting injured player
    * Transactions
        * Total number of transactions (by position, by team)
        * Waiver trends
        * Trade and Pickup Analysis
    * Future Value
        * Bench value
        * Draft picks
        * Average age of team by position
    * Streaks over 100 pts

  * Positional Strength
    * What are the positional strengths and weakness of each team? 
    * How have they changed over time?

  * Positional Impact  
    * How impactful are defense and kickers to the outcome of the league?
    * What are the most important positions?

  * Matchup Analysis
    * All time manager vs. manager matchups
    * All time all vs. all 
    * All time records
    * Luck Index (Spirit of WC)
    * Winning/Lossing Streaks
    
  * Case Studies
    * Is it possible to quantify how terrible Jim is as a human and as a fantasy football manager?
    * Is it possible to prove that my (Joe's) lack of success is due to a statistical anomaly? 

  * Oddball
    * How many team names is too many team names?
    


```{r Install Packages, include=FALSE}
ipak <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg)) 
        install.packages(new.pkg, dependencies = TRUE)
    suppressWarnings(suppressMessages(sapply(pkg, require, character.only = TRUE)))
}

ipak(c("tidyverse", "skimr", "kableExtra", "knitr"))

theme_set(theme_light())
scale_colour_discrete <- function(...) scale_colour_brewer(..., palette="Paired")
scale_fill_discrete <- function(...) scale_fill_brewer(... , palette="Paired")

```

```{r Load Data, include=FALSE}
df.stats <- read.csv("../Data/points.csv", header = TRUE)
df.sched <- read.csv("../Data/schedules.csv", header = TRUE)
```

```{r Change Data Types, include=FALSE}

#Convert stats dataframe
tmp.conv <- c("team_id", "manager_id", "player_id")
for (col in tmp.conv) {
  df.stats[,col] <- as.factor(df.stats[,col])
}

#Convert schedule dataframe
tmp.conv <- c("team_id", "team_id_opp", "matchup_type")
for (col in tmp.conv) {
  df.sched[,col] <- as.factor(df.sched[,col])
}

```

```{r Sort Data, include=FALSE}
df.stats <- df.stats %>%
  arrange(season, week, team_id, set_pos, player_pos, player_name)

df.sched <- df.sched %>%
  arrange(season, week, result)

```

```{r Team Reference Data, include=FALSE}

df.managers.short <- data.frame("manager_name" = c("AMackel", "CameronRouzer", "conorclarke", "dayello", "jimayello", "JoeDeGregorio", "M_Stojanovic", "SeanMcNally", "THaze", "TimMartens", "Truax", "WillPo", "zachzachzach"), 
                                "manager_name_short" = c("Aaron", "Cam", "Conor", "Dan", "Jim", "Joe", "Mike", "Sean", "Tom", "Tim", "Truax", "Will", "Zach"))

df.managers <- df.stats %>%
  select(manager_id, manager_name) %>%
  distinct() %>%
  arrange(manager_name) %>%
  left_join(df.managers.short, by = "manager_name")


df.teams <- df.stats %>%
  group_by(team_id) %>%
  arrange(season, week) %>%
  summarise(manager_id_cur = last(manager_id),
            manager_name_cur = last(manager_name),
            team_name_cur = last(team_name)) %>%
  left_join(df.managers %>% select(manager_id, manager_name_short),
            by = c("manager_id_cur" = "manager_id"))

```

# Team Performance

## Power Rankings

```{r}

#Gather plot data
tmp.plot <- df.stats %>%
  group_by(team_id, season, week) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  filter(as.integer(week) <= 13) %>%
  summarise(points_total = sum(points)) %>%
  ungroup() %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by="team_id") %>%
  select(Manager = manager_name_short,
         Season = season,
         Week = week,
         Points = points_total) %>%
  arrange(Season, Week) %>%
  mutate(Week = paste0(Season, "-", Week)) %>%
  mutate(Week = factor(Week, ordered = TRUE))

# Create Plot
p <- ggplot(tmp.plot, aes(x = as.integer(Week), y = Points, col = Manager)) +
  geom_smooth(method = 'loess', formula = 'y ~ x',level = 0.5, span = .8, alpha = 0.2) +
  geom_vline(xintercept = seq(13, as.integer(max(tmp.plot$Week)), 13), alpha = 0.2) +
  labs(title = paste("Power Rankings")) +
  xlab("Weeks") +
  ylab("Mean Points") +
  theme(plot.title = element_text(hjust = 0.5))

# Print Plot
print(p)
  
```

## Point Distribution

```{r fig.height=25, fig.width=10}
tmp.plot <- df.stats %>%
  left_join(df.managers %>% select(manager_id, manager_name_short), by="manager_id") %>%
  select(manager_name_short,
         season,
         week,
         set_pos,
         points) %>%
  filter(as.integer(week) <= 13) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  group_by(season, week, manager_name_short) %>%
  summarise(point_total = sum(points))

ggplot(tmp.plot, 
       aes(x = point_total, 
           fill = reorder(manager_name_short, 
                          point_total, 
                          mean))) +
  geom_density(alpha = 0.5, show.legend = FALSE) +
  facet_wrap( ~ manager_name_short, ncol=1)

```

## Goose Eggs

```{r}
tmp.plot.all <- df.stats %>%
  left_join(df.managers %>% select(manager_id, manager_name_short), by="manager_id") %>%
  select(manager_name_short,
         season,
         week,
         set_pos,
         player_name,
         points) %>%
  filter(as.integer(week) <= 13) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  group_by(manager_name_short) %>%
  summarise(count_all = n())

tmp.plot.ltz <- df.stats %>%
  left_join(df.managers %>% select(manager_id, manager_name_short), by="manager_id") %>%
  select(manager_name_short,
         season,
         week,
         set_pos,
         player_name,
         points) %>%
  filter(as.integer(week) <= 13) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  filter(points <= 0) %>%
  group_by(manager_name_short) %>%
  summarise(count_ltz = n()) %>%
  left_join(tmp.plot.all, by = "manager_name_short") %>%
  mutate(rate = count_ltz/count_all) %>%
  select(Manager = manager_name_short,
         Rate = rate)

#Plot team names
ggplot(tmp.plot.ltz, aes(x = reorder(Manager, Rate), 
                     y = Rate,
                     fill = Rate)) +
  geom_bar(stat = "identity", 
           alpha = 0.8) +
  scale_fill_gradient(low = "white", high = "firebrick4") +
  labs(title = "Goose Eggs, or worse...",
       subtitle = "Rate of Starts with Zero or Fewer Points") +
  xlab("Manager") +
  ylab("Goose Egg Rate") +
  scale_y_continuous(labels = scales::percent) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = "none") +
  coord_flip()


```

## Luck Index

COnsider the following functions

row_number(): equivalent to rank(ties.method = "first")

min_rank(): equivalent to rank(ties.method = "min")

dense_rank(): like min_rank(), but with no gaps between ranks

percent_rank(): a number between 0 and 1 computed by rescaling min_rank to [0, 1]

cume_dist(): a cumulative distribution function. Proportion of all values less than or equal to the current rank.

ntile(): a rough rank, which breaks the input vector into n buckets

```{r}

```


# Historical Matchups

## All-time H2H Records
```{r message=FALSE, warning=FALSE, include=FALSE}

# Gather Wins
tmp.plot.win <- df.sched %>%
  filter(result == "W") %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = "team_id") %>%
  rename(manager_home = manager_name_short) %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = c("team_id_opp" = "team_id")) %>%
  rename(manager_away = manager_name_short) %>%
  select(-team_id, -team_id_opp) %>%
  group_by(manager_home, manager_away) %>%
  summarize(Wins = n()) %>%
  spread(key = manager_away,
         value = Wins,
         fill = 0)

# Rename rows
rownames(tmp.plot.win) <- tmp.plot.win$manager_home
tmp.plot.win$manager_home <- NULL

# Gather Losses
tmp.plot.loss <- df.sched %>%
  filter(result == "L") %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = "team_id") %>%
  rename(manager_home = manager_name_short) %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = c("team_id_opp" = "team_id")) %>%
  rename(manager_away = manager_name_short) %>%
  select(-team_id, -team_id_opp) %>%
  group_by(manager_home, manager_away) %>%
  summarize(Losses = n()) %>%
  spread(key = manager_away,
         value = Losses,
         fill = 0)

# Rename rows
rownames(tmp.plot.loss) <- tmp.plot.loss$manager_home
tmp.plot.loss$manager_home <- NULL

# Merge
for (i in 1:nrow(tmp.plot.win)) {
  for (j in 1:ncol(tmp.plot.win)) {
    tmp.plot.win[i,j] <- paste(tmp.plot.win[i,j], tmp.plot.loss[i,j], sep = "-")
    tmp.plot.win[i,j] <- ifelse(j == i, "-", tmp.plot.win[i,j])
  }
}

```

```{r}
tmp.plot.win %>%
  kable() %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = F) %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = T) %>%
  row_spec(1:12, align = "center") %>%
  #cell_spec(tmp.plot.win$Jim, popover = spec_popover(content = "Jim Sucks")) %>%
  add_footnote(c("\n Rows represent the home team, columns are the away team", 
                 "Records shown with notation:  home-away"), 
               notation = "none")

```

## All-time H2H Point Differential
```{r message=FALSE, warning=FALSE, include=FALSE}

# Gather Wins
tmp.plot.win <- df.sched %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = "team_id") %>%
  rename(manager_home = manager_name_short) %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = c("team_id_opp" = "team_id")) %>%
  rename(manager_away = manager_name_short) %>%
  select(-team_id, -team_id_opp) %>%
  mutate(point_dif = score_team - score_opp) %>%
  group_by(manager_home, manager_away) %>%
  summarize(point_dif = round(sum(point_dif),0)) %>%
  spread(key = manager_away,
         value = point_dif)

# Rename rows
rownames(tmp.plot.win) <- tmp.plot.win$manager_home
tmp.plot.win$manager_home <- NULL


# Merge
for (i in 1:nrow(tmp.plot.win)) {
  for (j in 1:ncol(tmp.plot.win)) {
    tmp.plot.win[i,j] <- ifelse(j == i, "-", tmp.plot.win[i,j])
  }
}
```

```{r}
tmp.plot.win %>%
  kable() %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive"), full_width = F) %>%
  column_spec(1, bold = T) %>%
  row_spec(0, bold = T) %>%
  row_spec(1:12, align = "center") %>%
  #cell_spec(tmp.plot.win$Jim, popover = spec_popover(content = "Jim Sucks")) %>%
  add_footnote(c("\n Rows represent the home team, columns are the away team"), 
               notation = "none")
  
  

```

## All-time All vs. All Records

```{r include=FALSE}
# All Versus All Records
tmp.plot <- df.sched %>%
  left_join(df.teams %>% select(team_id, manager_name_short), by = "team_id") %>%
  select(season, week, manager_name_short, score_team) %>%
  group_by(season, week) %>%
  arrange(score_team) %>%
  mutate(week_wins = row_number()-1,
         week_losses = n() - week_wins) %>%
  ungroup() %>%
  group_by(manager_name_short) %>%
  summarise(wins = sum(week_wins),
            losses = sum(week_losses)) %>%
  arrange(desc(wins)) %>%
  select(Manager = manager_name_short, Wins = wins, Losses = losses)
```

```{r}
tmp.plot %>%
  kable() %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>%
  row_spec(0:12, align = "center") %>%
  column_spec(1, bold = T)
```


# Positional Strength

The following plots show the strength (mean weekly score of starters) of each position for each team. 

```{r Prepare Positional Strength Data, include=FALSE}

# Define Player Position Limits
df.pos.lim <- data.frame("player_pos" = c("QB", "RB", "WR", "TE", "K", "D/ST"),
                         "pos_lim" = c(1,2,3,1,1,1))

# Initialize data frame for collecting starter results
df.stats.toppos <- data.frame()

# Gather stats from top n starters from each position
for (i in 1:nrow(df.pos.lim)) {
  
  #Define position/limit for each player position
  pos = df.pos.lim[i, "player_pos"]
  lim = df.pos.lim[i,"pos_lim"]
  
  # Filter and select top n players
  tmp.stats.toppos <- df.stats %>%
    filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
    filter(player_pos == pos) %>%
    filter(as.integer(week) <= 13) %>%
    group_by(team_id, season, week) %>%
    top_n(lim, points) %>%
    ungroup() %>%
    left_join(df.teams %>% select(team_id, manager_name_short), by="team_id") %>%
    select(Manager = manager_name_short,
           Season = season,
           Week = week,
           Position = player_pos,
           Player = player_name,
           Points = points)
  
  # Compile Results
  df.stats.toppos <- rbind(df.stats.toppos, tmp.stats.toppos)
}

# Initialize data frame for collecting starter results
df.stats.topben <- data.frame()

# Gather stats from top bench player for each position
for (i in 1:nrow(df.pos.lim)) {
  
  #Define position/limit for each player position
  pos = df.pos.lim[i, "player_pos"]
  lim = 1
  
  # Filter and select top n players
  tmp.stats.topben <- df.stats %>%
    filter(set_pos %in% c("BN", "TAXI")) %>%
    filter(player_pos == pos) %>%
    filter(as.integer(week) <= 13) %>%
    group_by(team_id, season, week) %>%
    top_n(lim, points) %>%
    ungroup() %>%
    left_join(df.teams %>% select(team_id, manager_name_short), by="team_id") %>%
    select(Manager = manager_name_short,
           Season = season,
           Week = week,
           Position = player_pos,
           Player = player_name,
           Points = points)
  
  # Compile Results
  df.stats.topben <- rbind(df.stats.topben, tmp.stats.topben)
}

```

## Starters
```{r fig.height=24, fig.width=12}

# Define temporary plot data
tmp.plot <- df.stats.toppos %>%
  filter(Position != "K") %>%
  arrange(Season, Week) %>%
  mutate(Week = paste0(Season, "-", Week)) %>%
  mutate(Week = factor(Week, ordered = TRUE))

# Define Year Labels
#years <- seq(round(max(tmp.plot$Week/13),0)

# Create Plot
p <- ggplot(tmp.plot, aes(x = as.integer(Week), y = Points, col = Position)) +
  geom_smooth(method = 'loess', formula = 'y ~ x',level = 0.5, span = .8, alpha = 0.2) +
  geom_vline(xintercept = seq(13, as.integer(max(tmp.plot$Week)), 13), alpha = 0.2) +
  theme_light() +
  labs(title = paste("Starting Positional Strength Over Time")) +
  xlab("Weeks") +
  ylab("Points") +
  ylim(c(0,30)) +
  theme(plot.title = element_text(hjust = 0.5))

p <- p + facet_wrap( ~ Manager, ncol=2)

# Print Plot
print(p)
  

```

## Bench
```{r fig.height=24, fig.width=12}

# Define temporary plot data
tmp.plot <- df.stats.topben %>%
  filter(! Position %in% c("K", "D/ST")) %>%
  arrange(Season, Week) %>%
  mutate(Week = paste0(Season, "-", Week)) %>%
  mutate(Week = factor(Week, ordered = TRUE))

# Create Plot
p <- ggplot(tmp.plot, aes(x = as.integer(Week), y = Points, col = Position)) +
  geom_smooth(method = 'loess', formula = 'y ~ x',level = 0.5, span = .8, alpha = 0.2) +
  geom_vline(xintercept = seq(13, as.integer(max(tmp.plot$Week)), 13), alpha = 0.2) +
  labs(title = paste("Bench Positional Strength Over Time")) +
  xlab("Weeks") +
  ylab("Points") +
  ylim(c(0,30)) +
  theme(plot.title = element_text(hjust = 0.5))

p <- p + facet_wrap( ~ Manager, ncol=2)

# Print Plot
print(p)
  
```

# Position Impact Analysis


## Positional Point Diffential
Compares the 
```{r}

# Define Player Position Limits
df.pos.lim <- data.frame("player_pos" = c("QB", "RB", "WR", "TE", "K", "D/ST"),
                         "pos_lim" = c(1,2,3,1,1,1))

tmp.plot <- df.stats %>%
  select(season,
         week,
         player_pos,
         set_pos,
         points) %>%
  left_join(df.pos.lim, by = "player_pos") %>%
  filter(as.integer(week) <= 13) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  group_by(season, week, player_pos) %>%
  arrange(desc(points)) %>%
  mutate(rank_pos = row_number(),
         rank = ifelse(rank_pos <= pos_lim*6, "Top", "Bottom")) %>%
  ungroup() %>%
  group_by(season, week, player_pos, rank) %>%
  summarise(points_mean = mean(points)) %>%
  spread(rank, points_mean) %>%
  mutate(points_dif = Top - Bottom) %>%
  select(Position = player_pos, `Point Differential` = points_dif)
  

ggplot(tmp.plot, aes(x = reorder(Position, `Point Differential`, median), y = `Point Differential`)) +
  geom_boxplot(alpha = 0.8, outlier.shape = NA) +
  geom_jitter(alpha = 0.6, width = 0.25, aes(col = Position)) +
  labs(title = paste("Mean Point Differential - Best vs. Worse Weekly")) +
  xlab("Positions") +  
  ylab("Mean Point Differential") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
  

```

## Match Outcome Impact Rate

```{r}

# Define Player Position Limits
df.pos.lim <- data.frame("player_pos" = c("QB", "RB", "WR", "TE", "K", "D/ST"),
                         "pos_lim" = c(1,2,3,1,1,1))

# Gaher player stats and ranked positions
tmp.stats <- df.stats %>%
  select(season,
         week,
         team_id,
         player_pos,
         set_pos,
         points) %>%
  left_join(df.pos.lim, by = "player_pos") %>%
  filter(as.integer(week) <= 13) %>%
  filter(! set_pos %in% c("BN", "IR", "TAXI")) %>%
  group_by(season, week, team_id, player_pos) %>%
  arrange(points) %>%
  mutate(rank = row_number()) %>%
  filter(rank <= pos_lim) %>%
  ungroup() %>%
  mutate(player_pos = as.character(player_pos),
         player_pos = ifelse(pos_lim > 1,
                             paste0(player_pos, rank),
                             player_pos)) %>%
  select(season, week, team_id, player_pos, points)
  
# Gather match point differntial each week
tmp.match <- df.sched %>%
  filter(result == "W",
         week <= 13) %>%
  select(season, week, team_id, team_id_opp, score_team, score_opp) %>%
  mutate(score_dif = score_team - score_opp,
         match_id = paste(team_id, team_id_opp, sep = "-")) %>%
  select(season, week, match_id, score_dif)

# Calculate ratios between player/match point differntials and determine outcome impact
tmp.plot <- df.sched %>%
  filter(result == "W",
         week <= 13) %>%
  select(season, week, team_id, team_id_opp) %>%
  mutate(match_id = paste(team_id, team_id_opp, sep = "-")) %>%
  gather(key = team_type, value = team_id, team_id, team_id_opp) %>%
  left_join(tmp.stats, by = c("season", "week", "team_id")) %>%
  mutate(points = ifelse(team_type == "team_id_opp", 
                         -points, 
                         points)) %>%
  group_by(season, week, match_id, player_pos) %>%
  summarise(points_dif = abs(sum(points))) %>%
  ungroup() %>%
  left_join(tmp.match, by = c("season", "week", "match_id")) %>%
  mutate(impact_rto = points_dif/score_dif,
         impact_result = impact_rto >= 1) %>%
  select(season, week, match_id, player_pos, impact_rto, impact_result) %>%
  rename(Position = player_pos, Ratio = impact_rto, `Impact Result` = impact_result) %>%
  group_by(Position) %>%
  summarise(impact_pct = sum(`Impact Result`)/n()) %>%
  ungroup()

  
# Plot
ggplot(tmp.plot, aes(x = reorder(Position, impact_pct), y = impact_pct, fill = impact_pct)) +
  geom_bar(stat = "identity", alpha = 0.8) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_gradient(low = "white", high = "firebrick4") +
  labs(title = "Matchup Outcome Impact by Position",
       subtitle = "Percentage of matchups where positional point difference\n would have changed the match outcome") +
  xlab("Positions") +  
  ylab("Percent Impact") +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.subtitle = element_text(hjust = 0.5), 
        legend.position = "none") +
  coord_flip()
  

```

# Other Odds and Ends

## Tightest Match and Biggest Whomping

```{r}
tmp.plot <- df.sched %>%
  filter(result == "W") %>%
  select(season, week, team_id, team_id_opp, score_team, score_opp) %>%
  mutate(score_dif = score_team - score_opp) %>%
```


## Team Names Insecurity 

```{r}

# Gather team name data
df.teamnames <- df.stats %>%
  select(manager_name, team_name) %>%
  distinct() %>%
  group_by(manager_name) %>%
  summarise(Count = n(),
            Names = paste0(team_name, collapse = ", ")) %>%
  arrange(desc(Count)) %>%
  rename(Manager = manager_name)

#Plot team names
ggplot(df.teamnames, 
       aes(x = reorder(Manager, Count), 
           y = Count)) +
  geom_bar(stat = "identity", 
           alpha = 0.8) +
  geom_text(aes(x = Manager, 
                y = 0.1, 
                label = Names, 
                hjust = 0, 
                vjust = 0.5), 
            size = 2.5, 
            col = "white") +
  labs(title = "Team Name Insecurity") +
  xlab("Manager") +
  ylab("Number of Team Names") +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_flip()

```

## Championship Losses to Rob Dvorak

```{r}
tmp.plot <- 
  data.frame("Manager" = c("Aaron", "Jim", "Tim", "Cam", "Sean", "Dan", "Will", "Truax", "Joe", "Tom", "Conor", "Zach"), 
             "Outcome" = c(2,-1,0,0,0,0,0,0,0,0,0,0), 
             "type" = c("W", "L", "L", "L", "L", "L", "L", "L", "L", "L", "L", "L"))

ggplot(tmp.plot, aes(x = reorder(Manager, abs(Outcome)), y = Outcome)) +
  geom_bar(stat = "identity", aes(fill = type), col = "black", alpha = 0.8) +
  geom_text(aes(x = "Jim", y = -0.5, label = "Jim is a failure."), col = "white") +
  geom_text(aes(x = "Aaron", y = 1, label = "Aaron did his job.  Twice..."), col = "white") +
  geom_text(aes(x = "Cam", y = 0.5, label = "Wins"), col = "black") +
  geom_text(aes(x = "Cam", y = -0.5, label = "Losses"), col = "black") +
  geom_vline(xintercept = 0) +
  theme_light() +
  scale_fill_manual(values=c("firebrick3", "forestgreen")) +
  labs(title = "Championship Outcomes vs. Rob Dvorak") +
  xlab("Manager") +
  ylab("Outcome") +
  ylim(c(-2,2)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_flip()


```



```{r}
# Cleanup Workspace=
rm(list = ls(pattern = "^tbl.|^tmp.|^con.|^pack.|^[:alpha::]$"))
```

